A Toolbox for Manipulating and Assessing Color Palettes

### 2020-11-05 pkg/colorspace/paper/Toolbox/article.Rmd
small touch-ups carried over from JSS paper
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@556 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

Moreover, the _grDevices_ package in base R gained a new function
`palette.colors()` [@color:grDevices2] that provides various
well-established qualitative color palettes that can not be approximated well by
`qualitative_hcl()` due to pronounced variations in luminance and chroma.
While a qualitative palette with fixed luminance and chroma is more balanced,
a certain amount of variations in these properties might be necessary to make
more colors distinguishable, especially for viewers with color vision deficiencies.
